Syntax and Semantics of Indexed Abstract Binding Trees

### 2015-11-08 paper.tex
restore Aczel's priority for unisorted abts

Abstract binding trees (abts) are a generalization of abstract syntax trees
where operators may express variable binding structure as part of their
arities.  Originally inspired by Martin-L\"of's theory of arities
\cite{martin-lof:1984}, unisorted abts have been deployed successfully as the
uniform syntactic framework for several implementations of Constructive Type
Theory, including Nuprl \cite{constable:1986}, MetaPRL \cite{hickey:2003} and
JonPRL \cite{jonprl:2015}.

>>>>

Abstract binding trees (abts) are a generalization of abstract syntax trees
where operators may express variable binding structure as part of their
arities.  Originally formulated by Peter Aczel \cite{aczel:1978}, unisorted
abts have been deployed successfully as the uniform syntactic framework for
several implementations of Constructive Type Theory, including Nuprl
\cite{constable:1986}, MetaPRL \cite{hickey:2003} and JonPRL
\cite{jonprl:2015}.
